---
title: "HW2_wenting_xu"
output: pdf_document
---
# Q1
## a.
Suppose ith dimension has $$L{i}$$ levels, the total number of cuboid is
$$\prod{(L{i} + 1)}$$
There are 10 dimensions with no hierarchy, so the number of cuboids are
```{r}
2^10
```
```{r}'
1024 cuboids are there in the full data cube
```
## b.
First, we consider at least one of the first three elements is not aggregated.
```{r}
(2^3 - 1)*2^7
```
There are 3 base cell.
```{r}
3 * 896
```

Then we consider that if the first three dimensions are all aggregated

```{r}
2^7
```

Since there are 3 base cells. So the number of cell is

```{r}
2688 + 128 - 3
```

```{r}'
The complete cube will contain 2813 distinct aggregated (i.e., non-base) cells.
```
## c.
when count > 2, it means we only consider the last 7 dimensions.

```{r}
2^7
```

```{r}'
An iceberg cube will contain 128 distinct aggregated cells, if the condition of the iceberg cube is count > 2.
```
## c.
only the last 7 dimensions can be counted 3
```{r}'
The closed cell with count = 3  has 7 non-star dimensions.
```


#Q2

##a 
Suppose ith dimension has $$L{i}$$ levels, the total number of cuboid is
$$\prod{(L{i} + 1)}$$
```{r}
3*2*2*2
```

##b

```{r}
data = read.csv("Q2data.csv",header = FALSE)
name = c("id","state","city","category","price","rating")
colnames(data) = name
```

```{r}
## sort
data = data[order(data[,3],data[,4],data[,5],data[,6]),]
```

```{r}
library(plyr)
nrow(count(data,vars = c("city","category","price","rating")))
```
```{r}'
There are 48 cells in the cuboid (Location(city), Category, Rating, Price).
```
## c
```{r}
nrow(count(data,vars = c("state","category","price","rating")))
```

```{r}'
There are 34 cells in the cuboid (Location(State), Category, Rating, Price).
```
## d

```{r}
nrow(count(data,vars = c("category","price","rating")))
```

```{r}'
There are 23 cells in the cuboid (* , Category , Rating , Price).
```

## e

```{r}
sum(data$state == "Illinois" & data$rating == 3 & data$price == "moderate")
```

```{r}'
The count for the cell (Location(state) = ’Illinois’ , * , rating = 3 , Price = ’Moderate’) is 2.
```
## f

```{r}
sum(data$city == "Chicago" & data$category == "food")
```

```{r}'
The count for the cell (Location(city) = ’Chicago’ , Category=’food’ , * , *) is 2
```

# Q3

## a. support = 20

### 1.
```{r echo = FALSE, eval = FALSE}
install.packages("arules")
```

```{r}
library("arules")
tr = read.transactions("Q3data",format="basket",sep=" ")
```

```{r}
frequentItems = eclat (tr, parameter = list(supp = 0.2))
```


```{r}
length(frequentItems)
```

```{r}‘
The number of frequent patterns is 30
```

### 2.

```{r}
frequentItems <- eclat (tr, parameter = list(supp = 0.2,maxlen = 3, minlen = 3))
length(frequentItems)
```

```{r}’
The number of frequent patterns with length 3 is 8
```

###3
```{r}
rules <- apriori(tr, 
                 parameter = list(supp = 0.2, target = "rules"))
maximal = is.maximal(rules)
length(rules[maximal])
```

```{r}'
The number of max patterns is 7
```

## b. support = 10
### 1
```{r}
frequentItems_10 = eclat (tr, parameter = list(supp = 0.1))
length(frequentItems_10)
```
```{r}'
The number of frequent pattern is 55.
```


### 2

```{r}
frequentItems_10_3 = eclat (tr, parameter = list(supp = 0.1,maxlen = 3, minlen = 3))
length(frequentItems_10_3)
```
```{r}'
The number of frequent patterns with length 3 is 20
```


### 3

```{r}'
Calculate the number of maximal patterns
```


```{r}
maximal = is.maximal(frequentItems_10)
length(frequentItems_10[maximal])
```
###4
```{r}
frequentItems = apriori(tr, parameter = list(supp = 0.1,conf = 0,maxlen = 3,minlen = 3))
```


```{r}
round(quality(frequentItems[60])$confidence,3)
```
According to the formula:
$$P(A|C\cap E) = \frac{P(A\cap C\cap E)}{P(C\cap E))}$$

```{r}'
the confidence measure of the association rule (C, E) -> A is 0.679
```

###5
```{r}
frequentItems = apriori (tr, parameter = list(supp = 0.1,conf = 0,maxlen = 4, minlen = 4))
```

```{r}
round(quality(frequentItems[34])$confidence,3)
```
According to the formula:
$$P(E|A\cap B\cap C) = \frac{P(A\cap B\cap C\cap E)}{P(A\cap B\cap C))}$$

```{r}‘
the confidence measure of the association rule (A, B, C) -> E is 0.742
```


